\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-06-10 draft.tex
explain no timing change, add footnote to text; closes #21

Next, nature determines with probabilities $o$ and $o^*$ whether each legislature will have the opportunity to take a vote to break the agreement. I assume that these probabilities are less than one-half and mutually exclusive.\footnote{While this assumption is made for purposes of exposition and tractability, one can think of $o$ and $o^*$ as being determined by events beyond the executives' or legislatures' control that determine whether or not the legislatures will be willing to consider the lobby's request; for example, they would be affected by the occurrence of an economic crisis that diverts the legislature's attention from less-pressing matters.} This allows me to focus on the key interaction between the domestic actors and abstract from the strategic interaction between the lobbies in the two countries.\footnote{When the legislatures in both countries have an opportunity to break the agreement simultaneously, an incentive for each lobby to free ride on the effort of the other makes the optimization problem of the executives more complex as they are faced with the problem of how best to exploit the free-riding dynamic.}

>>>>

Next, nature determines with probabilities $o$ and $o^*$ whether each legislature will have the opportunity to take a vote to break the agreement. I assume that these probabilities are less than one-half and mutually exclusive.\footnote{While this assumption is made for purposes of exposition and tractability, one can think of $o$ and $o^*$ as being determined by events beyond the executives' or legislatures' control that determine whether or not the legislatures will be willing to consider the lobby's request; for example, they would be affected by the occurrence of an economic crisis that diverts the legislature's attention from less-pressing matters.} This allows me to focus on the key interaction between the domestic actors and abstract from the strategic interaction between the lobbies in the two countries.\footnote{When the legislatures in both countries have an opportunity to break the agreement simultaneously, an incentive for each lobby to free ride on the effort of the other makes the optimization problem of the executives more complex as they are faced with the problem of how best to exploit the free-riding dynamic. \textbf{Alternatively, one can take the break decisions in the two countries to be sequential with the executives behind a veil of ignorance about which legislature will move first. In that set up, the end results are the same as in the current model but additional intermediate results are needed.}}

### 2016-06-10 letter-round2.tex
explain no timing change, add footnote to text; closes #21

  \item \textit{I don't see how the move of Nature (which determines the probabilities o and o* is consistent with the idea that there is uncertainty about who is the median voter (which was part of your motivation). Assuming that o and o* are mutually exclusive is not great. It would be better to assume some timing (rather than have a simultaneous choice). Since the game is symmetric, assuming that Home’s legislature moves before Foreign's would be without further loss of generality.}
  \item \textit{``the uncertainty about the median legislator's identity is resolved.'' What is this uncertainty really about?} \\
	This is explained in Section [currently 2.4, but will move], so I did not repeat it or reference it here in line with the earlier stylistic advice.

>>>>

  \item \textit{I don't see how the move of Nature (which determines the probabilities o and o* is consistent with the idea that there is uncertainty about who is the median voter (which was part of your motivation). Assuming that o and o* are mutually exclusive is not great. It would be better to assume some timing (rather than have a simultaneous choice). Since the game is symmetric, assuming that Home’s legislature moves before Foreign's would be without further loss of generality.} \\
	I view the move of nature that determines the probabilities $o$ and $o^*$ as distinct from the uncertainty about the identity of the median legislator. This is really just a theoretical device to simplify the model.

	The sequential model you suggested is very attractive. I worked it out and wrote it into the draft. All the results go through (with one small additional assumption on magnitudes: it must be ensured that the lobby's direct response to an increase in trade agreement tariffs is stronger than a new effect wherein the lobby might increase effort to compensate for the trading partner's legislature reducing its break probability in response to that same tariff increase). However, the model is significantly complicated as two actors have to be modeled and results added since they can no longer be accounted for by symmetry. This added considerable length without compensating insight, so I opted to add a footnote explaining the near-equivalence of the models in line with your desire to simplify the presentation and not distract from the central point. The new text reads as follows can can be found in \textbf{Footnote ??? on Page???}:
	\begin{quote}
		Alternatively, one can take the break decisions in the two countries to be sequential with the executives behind a veil of ignorance about which legislature will move first. In that set up, the end results are the same as in the current model but additional intermediate results are needed.
	\end{quote}

  \item \textit{``the uncertainty about the median legislator's identity is resolved.'' What is this uncertainty really about?} \\
	This is explained in Section [currently 2.4, but will move], so I did not repeat it or reference it here in line with the earlier stylistic advice.
